% !TEX root = ../report.tex
\begin{abstract}
    Control-bounded conversion is a conceptually new approach to A/D conversion, that extends the possibilities for what an A/D converter could be. Of special interest in this thesis, is how a control-bounded ADC could be used advantageously in receiver systems with multiple input channels. The underlying motivation is to utilize prior information about the input signal to achieve increased performance. We argue that, in a multi-channel receiver system, placing several independent, general purpose ADCs, side-by-side, is not likely the most efficient way of capturing the incoming information. The control-bounded conversion principle enables a new approach to the design of a multi-channel receiver system.

    The main contribution of this thesis is a proposed ADC architecture, which allows for a more power efficient implementation of the previously introduced Hadamard ADC. This architecture is evaluated on an architectural level and potential implementation challenges are discussed. A simulation verifies that this architecture dramatically reduces harmonics in the spectrum under the presence of component mismatch. Another interesting feature of this architecture is the ability to utilize an uneven energy distribution between the different input channels. For a receiver with e.g. 1000 channels, this would give a direct SNR increasement of up to 30dB. The achievable SNR gain will depend on the application.

    In addition to the proposed architecture, a simpler structure based on a chain of integrators is also considered. Some of the features that is presented together with the proposed architecture, could also be applied to this simpler system. In consequence, the thesis presents two very different architectures that both allow for new ways of utilizing the properties of a multi-channel receiver system. Some associated design challenges for each of them are also discussed. We hope that this thesis provides a useful background for choosing an appropriate control-bounded ADC architecture, considering the application at hand.
\end{abstract}

